---
title: "Who does more pushups"
author: "your name"
date: "March 8"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r include=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?

The data collected by the MAT 111 students is for 30 players, 22 of them are skill players and 8 of them are line players. They recorded their weights and the amount of pushups they did under 2 minutes.
# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
For my graphical method, I will use a boxplot to show the spread of the discrete data (pushups) to determine which group has the highest data set. As for numerics, conducting the t test will tell us if these groups prform differently from eachother.





# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
In my results, we are going to see through a boxplot that skill players preform more pushups on average than line players. The t test will show us if there are significant differences between these groups. 

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
```{r include=FALSE}
boxplot(pushups ~ position, data = pushups)
```

In the box the line and skill players are divded into two catgories. We can see that the skill players have a higher midspread (box) of pushups, whereas the line players have a lower midspread (box) of pushups--including the minnimum at 6. The skill players show an outlier with the dot, which is the max at 108.

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
t.test(pushups$pushups)
```

In the t, test the p-value computed was 6.651e-10 which is approximatley 0.000000000651. The p-value suggest to us that there is significnt differences between the averages in both groups, meaning one did better than the other.

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

<strike>$H:_0$ There is no significant difference between the average of pushups preformed by line players and skill players.</strike>

$H:_A$ There is significant differences between the average of pushups preformed by line players and skill players.

In the t.test, the p-value is less than than 0.05 which suggests to us that there are sigificant diffrences between the data in both groups, and we have evidence for the alterative hypothesis. In addition, we fail to accept the null hypothesis as true. 

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

In this study to find out who does more pushups, averages were collected from 30 players, then the data was used to construct a box plot to visually compare the groups: the skill players preformed better than linemen. After, a t test was conducted to test the significance of the averages of both groups. It computed a p-value less than 0.05, which suggested that there is evidence for the alternative hypothesis--and fail to accept the null as true. The alternative hypothesis is there is significant differences between the average of pushups preformed by line players and skill players. Therefore, we can conclude that the answe to the research question is that skill players do more pushups, on average.
